---
title: "tutorialTK"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tutorialTK)
data(cbb8)

library(ggplot2)
library(cowplot)
library(magrittr)
```

This repository contains the R package, tutorialTK, that has some functions and data that I find helpful when writing tutorials and presentations. Here are some use cases:

## Installation

```{r install, eval=FALSE}
library(devtools)
install_github("johnsonra/tutorialTK")
```

## Colorblind-friendly pallete

I have a couple of colorblind-friendly palletes I've included with this package.

```{r iris example}
library(datasets)

princomp(iris[,1:4])$scores %>%
    cbind(iris) %>%
    
    ggplot(aes(Comp.1, Comp.2, color = Species)) +
    geom_point() +
    scale_color_manual(values = cbb8[1:3])
```

## Ghostwriter

If you find yourself trying to think, talk and type at the same time while recording a tutorial, `ghostwriter` might be a good tool for you. Start by putting the text you want to type into a file (e.g. `code.txt`), and have `ghostwriter` write an AppleScript file to do the typing for you (sorry, Linux and Windows users - any similar solutions for those systems is welcome).

```{r ghostwriter example}
ghostwriter('code.txt')
```

Here is an example of a `ghostwriter` script typing while I talk.

<iframe src="https://drive.google.com/file/d/1JHJKxQZJro42fUlZjOCbCj-hwn8f7k8C/preview" width="640" height="480"></iframe>
